A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2017-05-18 meth.tex
updating cov with better threshold

Variability of the historical trajectory is also an important characteristic
when considering the choice of harmonization method. Such trajectories are
normally indicative of emissions from land use sectors. Land use sectors are
modeled with varying fidelity by IAMs, but in general proxies are used for
emissions trajectories. Take for example the emissions of black carbon (BC) from
grassland burning in Africa \TODO{check that this is a good sector}: for most
models, the use of grass and paturelands is modeled, and the emissions of
species from the burning of these lands is determined by applying a emissions
factor to a proxy model of burning of these lands; in general, the more
grassland usage occurs, the higher the emissions from burning of
grasslands. Therefore, consistency in harmonization method is important due to
the approaches taken in modeling these sectors by IAMs. In order to reliably
detect land-use-like emissions, a measure of the covariance of the historical
trajectory is calculated as shown in Equation \ref{eqs:cov} and tested against a
threshold. To determine this threshold, an analysis of the recent CEDS
\TODO{cite ceds paper} historical data has been performed. Figure \ref{fig:cov}
shows the distribution of land-use covariances and non-land-use covariances as
determined for historical data aggregated to 11 world regions \TODO{list regions
  for 11 regions}. A threshold value of 10 has been chosen based on the
11-region observations, but, importantly, any regional aggregation is possible
as this is model depedent.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{cov.pdf}
    \caption[]{
      \label{fig:cov}
      The distribution of $\Omega$ values for LUC and non-LUC historical
      trajectories are shown. The CEDS historical data is used for non-LUC data
      and \TODO{cite LUC data} is used for LUC data. All historical data has
      been aggregated to the 11-RCP \TODO{correct nomenclature?, cite} regions,
      and all gas species included in the historical datasets are included. The
      solid black line indicates the threshold value chosen in this analysis.
    }
  \end{center}
\end{figure}

>>>>

Variability of the historical trajectory is also an important characteristic
when considering the choice of harmonization method. Such trajectories are
normally indicative of emissions from land use sectors. Land use sectors are
modeled with varying fidelity by IAMs, but in general proxies are used for
emissions trajectories. Take for example the emissions of black carbon (BC) from
grassland burning in Africa \TODO{check that this is a good sector}: for most
models, the use of grass and paturelands is modeled, and the emissions of
species from the burning of these lands is determined by applying a emissions
factor to a proxy model of burning of these lands; in general, the more
grassland usage occurs, the higher the emissions from burning of
grasslands. Therefore, consistency in harmonization method is important due to
the approaches taken in modeling these sectors by IAMs. In order to reliably
detect land-use-like emissions, a measure of the covariance of the historical
trajectory is calculated as shown in Equation \ref{eqs:cov} and tested against a
threshold. To determine this threshold, an analysis of the recent CEDS
\TODO{cite ceds paper} historical data has been performed. Figure \ref{fig:cov}
shows the distribution of land-use covariances and non-land-use covariances as
determined for historical data aggregated to the model regions of 5 different
flagship IAMs \TODO{cite all 5 IAMs}. A threshold value of 20 has been chosen
based on these observations. Importantly, tails of the LUC and non-LUC overlap,
thus there are both false positives (~10\% of non-LUC trajectories) and false
negatives (~7\% of LUC trajectories). However, as any regional definition is
model depedent and thus any regional aggregation is possible an automated
detection mechanism is necessary.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{cov.pdf}
    \caption[]{
      \label{fig:cov}
      The distribution of $\Omega$ values for LUC and non-LUC historical
      trajectories are shown. CEDS historical data is used for non-LUC data and
      \TODO{cite LUC data} is used for LUC data. All historical data has been
      aggregated from countries to IAM model regional definitions, and all gas
      species included in the historical datasets are included in the
      analysis. The solid black line indicates the threshold value used by
      default in \code{aneris}.  
    }
  \end{center}
\end{figure}
